---
title: "Project Webscraping"
author: "Andrew Skemp and Henry Fisher"
date: "12/1/2022"
output:
  pdf_document:
    fig_height: 3
    fig_width: 4.5
  html_document: default
word_document: default
editor_options: 
  chunk_output_type: console
---

```{r}
library(tidyverse)
library(stringr)
library(httr)
library(rvest)
```

hundred meter nationals race tibbles

```{r}
hundredMeter <- read_html('https://tfrrs.org/results/75041/4566001/NCAA_Division_III_Outdoor_Track__Field_Championships/Mens-100-Meters')

hundred <- html_nodes(hundredMeter, css = "table")
hundred_final_mens <- html_table(hundred, header = TRUE, fill = TRUE)[[1]] %>%
  mutate(wind = "1.7",
         date = make_date(year = 2022L, month = 5L, day = 28L),
         meet = "NCAA Division III Outdoor Track & Field Championships") %>%
  rename(place = PL,
         name = NAME,
         class = YEAR,
         school = TEAM,
         time = TIME,
         score = SC)

hundred_prelims_mens <- html_table(hundred, header = TRUE, fill = TRUE)[[2]] %>%
  mutate(date = make_date(year = 2022L, month = 5L, day = 26L),
         meet = "NCAA Division III Outdoor Track & Field Championships") %>%
  rename(place = PL,
         name = NAME,
         class = YEAR,
         school = TEAM,
         time = TIME,
         wind = WIND)
hundred_final_mens
hundred_prelims_mens
write_csv(hundred_final_mens, "~/Mscs 264 F22/Project/Henry_Andrew/Data/hundred_final_mens.csv")
write_csv(hundred_prelims_mens, "~/Mscs 264 F22/Project/Henry_Andrew/Data/hundred_prelims_mens.csv")
```

fifteen hundred meter nationals race tibble

```{r}
fifteenMeter <- read_html('https://tfrrs.org/results/75041/4566013/NCAA_Division_III_Outdoor_Track__Field_Championships/Mens-1500-Meters')
fifteen <- html_nodes(fifteenMeter, css = "table")
fifteen_final_mens <- html_table(fifteen, header = TRUE, fill = TRUE)[[1]] %>%
  mutate(date = make_date(year = 2022L, month = 5L, day = 28L),
         meet = "NCAA Division III Outdoor Track & Field Championships",
         TIME = period_to_seconds(ms(TIME))) %>%
  rename(place = PL,
         athlete = NAME,
         class = YEAR,
         school = TEAM,
         time = TIME,
         score = SC)
fifteen_prelims_mens <- html_table(fifteen, header = TRUE, fill = TRUE)[[2]] %>%
  mutate(date = make_date(year = 2022L, month = 5L, day = 26L),
         meet = "NCAA Division III Outdoor Track & Field Championships",
         TIME = period_to_seconds(ms(TIME))) %>%
  rename(place = PL,
         athlete = NAME,
         class = YEAR,
         school = TEAM,
         time = TIME)
fifteen_final_mens
fifteen_prelims_mens
write_csv(fifteen_final_mens, "~/Mscs 264 F22/Project/Henry_Andrew/Data/fifteen_final_mens.csv")
write_csv(fifteen_prelims_mens, "~/Mscs 264 F22/Project/Henry_Andrew/Data/fifteen_prelims_mens.csv")
```

Team scores

```{r}
teamScores <- read_html('https://tfrrs.org/results/75041/NCAA_Division_III_Outdoor_Track__Field_Championships')
team_scores <- html_nodes(teamScores, css = "table")
final_team_scores_mens <- html_table(team_scores, header = TRUE, fill = TRUE)[[3]]
final_team_scores_womens <- html_table(team_scores, header = TRUE, fill = TRUE)[[4]]
final_team_scores_womens
final_team_scores_mens

write_csv(final_team_scores_mens, "~/Mscs 264 F22/Project/Henry_Andrew/Data/final_team_scores_mens.csv")
```

list of d3 schools by state

```{r}
Locations <- read_html('https://www.ncsasports.org/division-3-colleges')
schools <- Locations %>% 
  html_nodes(".container link+ div") %>%
  html_text()
schools

school_locations <- Locations %>%
  html_nodes('.container link~ div:nth-child(3)') %>%
  html_text()
school_locations

private <- Locations %>%
  html_nodes("meta+ .container div:nth-child(4)") %>%
  html_text()
private

conference <- Locations %>%
  html_nodes("meta+ .container div:nth-child(5)") %>%
  html_text()
conference

school_data1 <- tibble(schools, school_locations, private, conference) %>%
         mutate(schools = str_remove(schools, "University "),
                schools = str_remove(schools, "of "),
                schools = str_replace(schools, "Wisconsin – ", "Wis.-"),
                schools = str_trim(schools, side = "both"),
                schools = str_remove(schools, " University"),
                schools = str_replace(schools, "– Minnesota", "(Minn.)"),
                schools = str_remove(schools, "Massachusetts Institute Technology – "),
                schools = str_replace(schools, "Washington", "Washington U."),
                schools = str_remove(schools, " s"),
                schools = str_remove(schools, "The "),
                schools = str_replace(schools, "Steubenville", "(Ohio)"),
                schools = str_remove(schools, " Reserve"),
                schools = str_replace(schools, "Saint", "St."),
                schools = str_replace(schools, "Worcester Polytechnic Institute", "WPI"),
                schools = str_replace(schools, "Benedictine", "Benedictine (Ill.)"),
                schools = str_replace(schools, " State", " St."),
                schools = str_replace(schools, "California ", "Cal "),
                schools = str_replace(schools, "Carroll", "Carroll (Wis.)"),
                schools = str_replace(schools, "Catholic America", "Catholic"),
                schools = str_replace(schools, "Concordia – Texas", "Concordia (Tex.)"),
                schools = str_replace(schools, "Concordia College (Minn.)", "Concordia-Moorhead"),
                schools = str_replace(schools, "Adrian College", "Adrian"),
                schools = str_replace(schools, "Albion College", "Albion"),
                schools = str_replace(schools, "Bates College", "Bates"),
                schools = str_replace(schools, "Bethany Lutheran College", "Bethany Lutheran"),
                schools = str_replace(schools, "Birmingham-Southern College", "Birmingham-Southern"),
                schools = str_replace(schools, "Bridgewater College", "Bridgewater (Va.)"),
                schools = str_replace(schools, "SUNY College at Brockport", "Brockport St."),
                schools = str_replace(schools, "Carleton College", "Carleton"),
                schools = str_replace(schools, "Carthage College", "Carthage"),
                schools = str_replace(schools, "Centre College", "Centre"),
                schools = str_replace(schools, "Claremont-Mudd-Scripps Colleges", "Claremont-Mudd-Scripps"),
                schools = str_replace(schools, "Colby College", "Colby"),
                schools = str_replace(schools, "Elizabethtown College", "Elizabethtown"),
                schools = str_replace(schools, "Geneva College", "Geneva"),
                schools = str_replace(schools, "Grove City College", "Grove City"),
                schools = str_replace(schools, "Haverford College", "Haverford"),
                schools = str_replace(schools, "Hope College", "Hope"),
                schools = str_replace(schools, "Ithaca College", "Ithaca"),
                schools = str_replace(schools, "John Carroll (Wis.)", "John Carroll"),
                schools = str_replace(schools, "Knox College", "Knox"),
                schools = str_replace(schools, "Lebanon Valley College", "Lebanon Valley"),
                schools = str_replace(schools, "Lewis & Clark College", "Lewis & Clark"),
                schools = str_replace(schools, "Loras College", "Loras"),
                schools = str_replace(schools, "McDaniel College", "McDaniel"),
                schools = str_replace(schools, "Middlebury College", "Middlebury"),
                schools = str_replace(schools, "Millsaps College", "Millsaps"),
                schools = str_replace(schools, "Monmouth College", "Monmouth (Ill.)"),
                schools = str_replace(schools, "Montclair (St.)", "Montclair State"),
                schools = str_replace(schools, "North Central College", "North Central (Ill.)"),
                schools = str_replace(schools, "Olivet College", "Olivet"),
                schools = str_replace(schools, "Plymouth St.", "Plymouth State"),
                schools = str_replace(schools, "Pomona-Pitzer Colleges", "Pomona-Pitzer"),
                schools = str_replace(schools, "Principia College", "Principia"),
                schools = str_replace(schools, "Penn St. Behrend", "PSU-Behrend"),
                schools = str_replace(schools, "Ramapo College", "Ramapo"),
                schools = str_replace(schools, "Rhodes College", "Rhodes"),
                schools = str_replace(schools, "Ripon College", "Ripon"),
                schools = str_replace(schools, "Rochester Institute Technology", "RIT"),
                schools = str_replace(schools, "Rose-Hulman Institute Technology", "Rose-Hulman"),
                schools = str_replace(schools, "Rutgers, St. Univ. New Jersey, Camden", "Rutgers-Camden"),
                schools = str_replace(schools, "Rutgers – Newark", "Rutgers-Newark"),
                schools = str_replace(schools, "Simpson College", "Simpson (Iowa)"),
                schools = str_replace(schools, "Springfield College", "Springfield"),
                schools = str_replace(schools, "St. John Fisher College", "St. John Fisher"),
                schools = str_replace(schools, "St. Olaf College", "St. Olaf"),
                schools = str_replace(schools, "College St. Scholastica", "St. Scholastica"),
                schools = str_replace(schools, "College New Jersey", "TCNJ"),
                schools = str_replace(schools, "Massachusetts – Dartmouth", "UMass Dartmouth"),
                schools = str_replace(schools, "Wartburg College", "Wartburg"),
                schools = str_replace(schools, "Washington U. & Lee", "Washington and Lee"),
                schools = str_replace(schools, "Washington U. in St. Louis", "Washington U."),
                schools = str_replace(schools, "Westminster College – Pennsylvania", "Westminster (Pa.)"),
                schools = str_replace(schools, "Wheaton College – Illinois", "Wheaton (Ill.)"),
                schools = str_replace(schools, "Whittier College", "Whittier"),
                schools = str_replace(schools, "Williams College", "Williams"),
                schools = str_replace(schools, "Wilmington College", "Wilmington (Ohio)"),
                schools = str_replace(schools, "Wisconsin Lutheran College", "Wisconsin Lutheran"),
                schools = str_replace(schools, "College Wooster", "Wooster"),
                schools = str_replace(schools, "Bowdoin College", "Bowdoin"),
                schools = str_replace(schools, "SUNY Cortland", "Cortland St."),
                schools = str_replace(schools, "Rensselaer Polytechnic Institute – RPI", "RPI"),
                schools = str_replace(schools, "Babson College", "Babson")) %>%
  rename(school = schools)

#originally we removed all the " College" strings from the school names, but that caused other problems so I had to go back and do this manually for the 60-ish schools here.

#some of the str_replaces aren't working and I have no idea why, so I'm just going to replace the eight schools by hand because I think that will take less time

additional_school_names <- c("Alfred State", "Concordia-Moorhead", "John Carroll", "Pacific (Ore.)",
                             "Trinity (Conn.)", "Trinity (Tex.)", "U. of Chicago", "Wis.-Stout")

additional_school_locations <- c("Alfred, New York", "Moorhead, Minnesota", "University Heights, Ohio",
                                 "Forest Grove, Oregon", "Hartford, Connecticut", "San Antonio, Texas",
                                 "Chicago, Illinois", "Stout, Wisconsin")

additional_school_affiliation <- c("Public", "Private", "Private", "Private",
                                   "Private", "Private", "Private", "Public")

additional_school_conferences <- c("Allegheny Mountain Collegiate Conference",
                                   "Minnesota Intercollegiate Athletic Conference",
                                   "Ohio Athletic Conference",
                                   "Northwest Conference",
                                   "New England Small College Athletic Conference",
                                   "Southern Collegiate Athletic Conference",
                                   "University Athletic Association",
                                   "Wisconsin Intercollegiate Athletic Conference")

additional_school_data <- data.frame(additional_school_names, additional_school_locations,
                                     additional_school_affiliation, additional_school_conferences) %>%
  rename(school = additional_school_names,
         school_locations = additional_school_locations,
         private = additional_school_affiliation,
         conference = additional_school_conferences)

school_data <- rbind(school_data1, additional_school_data)

#Alfred State and Wis.-Stout don't exist at all in the school dataset (Wis.-Stevens Point is duplicated though), so I have to google the information for this

anti_join(individual_qualifiers, school_data) %>%
  count(school) %>%
  print(n = Inf)
  

write_csv(school_data, "~/Mscs 264 F22/Project/Henry_Andrew/Data/school_data.csv")
```

I had to tidy the data up pretty well. Did the best I could, but couldn't get all of the strings the same and would have had to manually go into each and change each. I think this should work. 

```{r}
Geographical_mens <- inner_join(final_team_scores_mens, school_data, by = c("TEAM" = "schools")) %>%
  print(n = Inf)
Geographical_womens <-inner_join(final_team_scores_womens, school_data, by = c("TEAM" = "schools")) %>%
  print(n = Inf)
```

All-Americans

100 (contains data on all 60m, 100m, and outdoors 200m races run by all 8 All-Americans)
```{r}
hundred_all_americans <- read_csv("~/Mscs 264 F22/Project/Henry_Andrew/Data/hundred_all_americans.csv")
hundred_all_americans
```

Individual Champions
```{r}
individual_champions <- individual_finals %>%
  filter(rank == 1) %>%
  select(2:5,7,8)
write_csv(individual_champions, "~/Mscs 264 F22/Project/Henry_Andrew/Data/individual_champions.csv")
```

Individual All-Americans
```{r}
all_americans <- individual_finals %>%
  filter(rank < 9)
write_csv(all_americans, "~/Mscs 264 F22/Project/Henry_Andrew/Data/all_americans.csv")
```

```{r}


```

